The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-06-08 presentation.tex
targeting paternalism rules

\date{April 2023}

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
         \vfill\item Paternalism
     \end{itemize}
\end{frame}

@@

% \begin{frame}{Description}
% \label{consort}
% \begin{figure}[H]
%      \caption{Experiment description}
%     \label{exp_description}
% \begin{center}
%         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
%   \end{center}
% \end{figure}
% \hyperlink{experimental_integrity}{\beamerbutton{Details}}

@@

\begin{frame}
\textbf{Predictors of take-up : $\Pr(Take-up)$}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{Figuras/determinants_takeup_reg.pdf}
    \end{center}
    \end{figure}
\end{frame}

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

@@

   \vfill 
  \hyperlink{several_def_cost}{\beamerbutton{More}}

@@

\begin{frame}{Intermediate outcomes: forced-commitment}
\label{intermediate_outcomes}
 \begin{itemize}
     \item \vfill \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.

    \item \vfill \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
    \begin{itemize}
        \item Actually, among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery. They also visit the branch less: as if the commitment contract makes them realize they will end up losing pawn anyway, and stop paying early on.
    \end{itemize}
    \end{itemize}

   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
\end{frame}

@@

    \vfill \item \textbf{Low demand:} In spite of this, given the opportunity, only 11\% of borrowers chose commitment.   
    \begin{itemize}
       \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhuvok et. al. 2018).
    \end{itemize}

    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
    \pause \vfill \ item The distribution of TE (i.e. $Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment. However, it can be bounded using the two marginal dist $F_1$ and $F_0$. \hyperlink{fan_park_bounds}{\beamerbutton{Fan \& Park bounds}}
    \vfill \item \textbf{Many with benefits did not demand:} We find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.
    \vfill \item Given our 3-armed experiment (+ imposing a mean exclusion restriction) allow us to estimate average TuT$>0$. %Furthermore, imposing the restriction for each cell of covariates and using Causal Forests gets us $F_{TUT}^{-1}(0.72)>0$.
    \end{itemize}
\end{frame}

@@

\vspace{.2in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. \{SQ,Com,Choice\}.  
    \item Treatment: $D \in \{0,1\} $, i.e. \{SQ,Com\}.
\end{itemize}

\vspace{.2in}
Assumptions:

\begin{itemize}
    \item $Z \independent (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$, i.e. \alert{being assigned to a contract has same effect as choosing it} (e.g. used in compulsory school attendance and returns to schooling lit).
\end{itemize}

\vspace{.2in}
Therefore:
\begin{itemize}
    \item  $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].$
\end{itemize}

\vspace{.2in}
Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     \item Also identified: $ASG:=ToT-TuT$, $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$, and $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$. 
\end{itemize}
\end{frame}

\begin{frame}{The ``Controlled Choice'' Design}
\label{cc_design}
\begin{itemize}
    \item Recall that under one-sided non-compliance (no always-takers), LATE=ToT.
\end{itemize}
\vspace{.2in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
    \end{center}
\end{figure}   
 \vfill
\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
\end{frame}

@@

\begin{frame}{Fraction that forgo benefit}

    \label{choose_wrong}

        \begin{figure}{\textwidth}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
        \end{figure}

\begin{itemize}
    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
    \item  $<$ 20\% of choosers made a mistake.
\end{itemize}

@@

\begin{frame}{Effects on clients coming back}

\begin{itemize}
    \item Client forced into commitment is 20\% more likely to come back again and pawn.
    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
    \item Conditional on recovery (endogenous), ``effect'' twice as big.
\end{itemize}

\vspace{.2in}
\begin{table}[H]
\begin{center}
\footnotesize{\input{./Tables/repeat_loans.tex}}
\end{center}
\end{table}    
\end{frame}

\begin{frame}{Learning}
    \label{learning_table}
    \begin{itemize}
    \item  Do people learn from Forced exposure to the program that they benefit from it?  
    \vspace{.1in}
    \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
    \vspace{.1in}
    \item  \textbf{No learning?} We don't find that being forced to the commitment contract makes them more likely to voluntarily chose commitment later.
    %\vfill \item Are people learning? \hyperlink{learning_table}{\beamerbutton{Table}}
 \end{itemize}  
 \vspace{.2in}
\begin{table}[H]
\begin{center}
\small{\input{./Tables/learning_exp_pres.tex}}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
        \onslide<1>{\item Discounting}
        \onslide<2-3>{\item Present-Bias}
    \end{itemize}
\vfill
\only<1>{  
 \begin{itemize}
 \item Can impatience explain why not take up a contract that decreases overall cost?
     \end{itemize}
\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).

\only<2>{

    \begin{itemize}
    \item   Standard behavioral angle:  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).  
    \end{itemize}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/hyperbolicity_strata.png}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item We have a survey measure of time inconsistency taken at baseline.
    \item  Effect of forcing commitment should be entirely among the time-inconsistent.  Is this true?  No, but PB measure may not be good.
    \end{itemize}
}

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1 or X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subpouplations have larger TuT.

\vspace{.3in}
    \begin{align*}
        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | D_i=0, X_i=1]}{TuT}\Pr(X_i=1 | D_i=0) \\
        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| D_i=0, X_i=0]}{TuT}\Pr(X_i=0 | D_i=0)
    \end{align*}

%and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
    \end{itemize}
}
\end{frame}

@@

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \vfill \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default might be embedded.
     \vfill \item Novel design to study essential heterogeneity: ``Controlled Choice''
        %\begin{itemize}
         %   \item Combine ``Controlled Choice'' with MTE: Can we extend results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs?
        %\end{itemize}
        \vfill \item  APR reduced by 34\% in the commitment arm
        \vfill  \item Results suggest selection on gains, but still large effects of imposing commitment on non-takers.
        \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.

        %\vfill \item   Are those with a greater experience of pawning less sure-confident?  
        \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
        \vfill\item Finally:  how to target and who would be hurt if we instituted  paternalism?

@@

\begin{frame}{Several definitions of cost}
\label{several_def_cost}
\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/fc_robustness_pres.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
    \hyperlink{main_results}{\beamerbutton{Back}}

@@

\begin{frame}{Intermediate outcomes}
\label{mechanism_appendix}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism1_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Intermediate outcomes}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism2_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

\begin{frame}{Intermediate outcomes}

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism3_pres.tex}}
\end{center}
\end{table}
\vfill
\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
\end{frame}

@@

>>>>

\date{June 2023}

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item \textbf{Experimental Design}
         \vfill\item Main results
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item Paternalism
     \end{itemize}
\end{frame}

@@

 \begin{frame}{Description}
 \label{consort}
 \begin{figure}[H]
      \caption{Experiment description}
     \label{exp_description}
 \begin{center}
         \includegraphics[width=0.80\textwidth]{Figuras/consort.pdf}
   \end{center}
 \end{figure}
 %\hyperlink{experimental_integrity}{\beamerbutton{Details}}

@@

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item \textbf{Main results}
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

\begin{frame}
\textbf{Predictors of take-up : $\Pr(Take up)=11\%$} on average.

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.9\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{center}
    \end{figure}
\end{frame}

@@

   \vfill 
  %\hyperlink{several_def_cost}{\beamerbutton{More}}

@@

\begin{frame}{Intermediate outcomes (1)}
\label{mechanism_appendix}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\scriptsize{\input{./Tables/mechanism1_pres.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.
\end{itemize}
\end{frame}

\begin{frame}{Intermediate outcomes (2)}

\begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism2_pres.tex}}
\end{center}
\end{table}

%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
   \vfill \item  \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
    \begin{itemize}
        \item Actually, among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery. They also visit the branch less: as if the commitment contract makes them realize they will end up losing pawn anyway, and stop paying early on.
    \end{itemize}
\end{frame}

\begin{frame}{Intermediate outcomes (3)}

    \begin{table}[H]
\caption{Intermediate outcomes}
\begin{center}
\footnotesize{\input{./Tables/mechanism3_pres.tex}}
\end{center}
\end{table}
\vfill
%\hyperlink{intermediate_outcomes}{\beamerbutton{Back}}
 \begin{itemize}
     \item \vfill \textbf{Frequency of visits:} Commitment induces a `parting of the waters' whereby those who were going to default visit the branch subsequently .2 fewer times.
\end{itemize}
\end{frame}

%\begin{frame}{Intermediate outcomes: forced-commitment}
%\label{intermediate_outcomes}
% \begin{itemize}
 %    \item \vfill \textbf{Speed of payment:} The first payment of the forced commitment contract  occurs 13 days earlier, increasing the fraction who recover on the first visit by 7.9 pp. Conditional on recovering, they recover 28 days faster.

  %  \item \vfill \textbf{Separating those who will not pay:} Commitment contract decreases fraction of borrowers making a payment and \textit{not} recovering by 7pp.
   % \begin{itemize}
    %    \item Actually, among those that default, those in the forced commitment arm are 14pp less likely to have paid towards recovery. They also visit the branch less: as if the commitment contract makes them realize they will end up losing pawn anyway, and stop paying early on.
    %\end{itemize}
    %\end{itemize}

  % \vfill

%   \hyperlink{mechanism_appendix}{\beamerbutton{Details}}
%\end{frame}

\begin{frame}{Costs fall from Forcing by multiple measures}
\label{several_def_cost}
\begin{table}[H]
\caption{Effects on several definitions of cost}
\label{table_robustness_fc}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/fc_robustness_pres.tex}}
}
\end{center}
 \scriptsize

%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}
   % \hyperlink{main_results}{\beamerbutton{Back}}
 \begin{itemize}
     \item \vfill Significantly reduced costs even when we include:
     \begin{itemize}
         \item Subjective rather than objective value of pawn.
         \item Travel costs.
         \item Valuing lost liquidity using the interest rate.
         \item All three at once.
     \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Do borrowers value Forcing as measured by repeat business?}

\vspace{.2in}
\begin{table}[H]
\begin{center}
\footnotesize{\input{./Tables/repeat_loans.tex}}
\end{center}
\end{table}    
\begin{itemize}
    \item Client forced into commitment is 20\% more likely to come back again and pawn.
    \item Not mechanically from having recovered the pawned, since also pawn other pieces.
    \item Not within the life of the loan, but after. So unlikely that is a liquidity story.
    \item Conditional on recovery (endogenous), ``effect'' twice as big.
\end{itemize}

@@

    \vfill \item \textbf{Low demand:} In spite of this, given the opportunity, only 11\% of borrowers chose commitment.   
    \begin{itemize}
       \pause \item If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had.
       \item However, we test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018).
    \end{itemize}

    \vfill \item The borrowers who did not choose commitment could simply be those who don’t need it?
    \pause \vfill \item The distribution of TE (i.e. $Y_{1i}-Y_{0i}$) is not identified, as one person is only observed in one treatment. However, it can be bounded using the two marginal dist $F_1$ and $F_0$.

\begin{frame}

\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\% }
    \label{fig:FanPark}
    \begin{center}
        \caption{APR}
        \centering
        \includegraphics[width=0.7\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{center}

%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\begin{itemize}
        \vfill \item \textbf{Many with benefits did not demand:} Making no parametric assumptions, we find that at least 30\% of individual borrowers benefit from commitment $\implies$ many did not demand even though TE is positive for them.

\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item Main results
          \vfill\item \textbf{Exploiting the Controlled Choice Design}
         \vfill\item Paternalism 
     \end{itemize}
\end{frame}

@@

Our 3-armed experiment + dual exclusion restriction allows us to estimate: 
\begin {itemize}
 \item Treatment Effect on the Treated (ToT), as with standard IV on one-sided non-compliance.
 \item Treatment on the Untreated (TUT), symmetric instrumentation for \textit{not} complying as compared to forcing arm.
\end{itemize}
\vspace{.2in}
Notation: 
\begin{itemize}
    \item Potential outcomes $(Y_0,Y_1,C)$
    \item Assignment: $Z \in \{0,1,2\}$, i.e. \{SQ,Com,Choice\}.  
    \item Treatment: $D \in \{0,1\} $, i.e. \{SQ,Com\}.
\end{itemize}

\vspace{.2in}

Assumptions:

\begin{itemize}
    \item $Z \independent (Y_0,Y_1,C)$, achieved by randomization
    \item $D = \mathbbm{1}(Z_i \neq 2) Z + \mathbbm{1}(Z_i=2) C$, i.e. \alert{being assigned to a contract has same effect as choosing it} (e.g. used in compulsory school attendance and returns to schooling lit).
\end{itemize}
\end{frame}

\begin{frame}{The Double Exclusion Restriction:}

With both of these exclusion restrictions in place:
\begin{itemize}
    \item Effect of (Control = Not Choosing) for non-choosers
    \item Effect of (Forcing = Choosing) for choosers.
    \end{itemize}
\begin{itemize}
    \item  $Y_i = \mathbbm{1}(Z_i =0) Y_{i0} + \mathbbm{1}(Z_i = 1)  Y_{i1}  + \mathbbm{1}(Z_i = 2) \left[(1 - C_i) Y_{i0} + C_i Y_{i1} \right].$
\end{itemize}

\vspace{.2in}

Prop:
\begin{itemize}
    \item ToT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 1)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=2) - \mathbbm{E}(Y_i|Z_i =0)}{\mathbbm{E}(D_i|Z_i=2)} $
     \item TuT := $\mathbbm{E}(Y_{i1} - Y_{i0} | C_i = 0)$ is point-identified, and equals $\frac{\mathbbm{E}(Y_i|Z_i=1) - \mathbbm{E}(Y_i|Z_i =2)}{1-\mathbbm{E}(D_i|Z_i=2)} $
     \item Also identified: 
     \begin{itemize}
         \item Average Selection on Gains $ASG:=ToT-TuT$
         \item Average Seletion Bias $ASB:= \E[Y_0 | C=1]-\E[Y_0 | C=0]$
         \item Average Selection on Levels $ASL:= \E[Y_1 | C=1]-\E[Y_1 | C=0]$
     \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{The ``Controlled Choice'' Design}
\label{cc_design}
\begin{itemize}
    \item Recall that under one-sided non-compliance (no always-takers), LATE=ToT.
\end{itemize}
\vspace{.2in}
\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=1.0\textwidth]{Figuras/tot_tut_intuition.png}
    \end{center}
\end{figure}   
 \vfill
%\hyperlink{identification_randomized_choice}{\beamerbutton{Identification}}
\end{frame}

@@

\section{Outline}
\begin{frame}{Outline}
     \begin{itemize}
         \vfill\item Experimental Design
         \vfill\item Main results
          \vfill\item Exploiting the Controlled Choice Design
         \vfill\item \textbf{Paternalism}
     \end{itemize}
\end{frame}

\begin{frame}{If commitment works, why don't people choose it?}
    \begin{itemize}
         \onslide<1>{\item Need to learn about it}
         \onslide<2>{\item Discounting}
        \onslide<3-4>{\item Present-Bias}
    \end{itemize}

\only<1>{

    \textbf{Do people learn from Forced exposure to the program that they benefit from it? } 
    \vspace{.1in}
    \begin{itemize}
    \item  Small sample (small power): focus on those that, after being either forced to commitment contract or to status quo, come back within a few months and are subject to choice arm.
    \vspace{.1in}
    \item  \textbf{No learning?} We don't find that being forced to the commitment contract makes them more likely to voluntarily chose commitment later.
    %\vfill \item Are people learning? \hyperlink{learning_table}{\beamerbutton{Table}}
 \end{itemize}  
 \vspace{.2in}
\begin{table}[H]
\begin{center}
\small{\input{./Tables/learning_exp_pres.tex}}
\end{center}
\end{table}
 %\hyperlink{learning}{\beamerbutton{Back}}
}

\vfill
\only<2>{

\textbf{Can impatience explain why not take up a contract that decreases overall cost?}

\begin{figure}[H]
        \caption{Financial cost for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.50\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item   Commitment contract imposes up-front costs for later benefits (collateral recovery).

 \textbf{Standard behavioral angle:}  compliers are sophisticated time-inconsistent, non-compliers are a mix of naifs and the time consistent (who don't need commitment).

\begin{figure}[H]
    \begin{center}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/hyperbolicity_strata.png}
    \end{center}
\end{figure}   
    \begin{itemize}
    \item We have a survey measure of time inconsistency taken at baseline.
    \item  Effect of forcing commitment should be entirely among the time-inconsistent.  Is this true?  No, but PB measure may not be good.
    \end{itemize}
}

\only<4>{

    \begin{itemize}
    \item   We estimate the TuT conditional on $X_i=1$ or $X_i=1$ (say $X_i= PB_i$ or $=Confidence_i$) and see which subppulations have larger TuT.

\vspace{.3in}
    \begin{align*}
        1=& \frac{\mathbb{E}[Y_{1i}-Y_{0i} | C_i=0, X_i=1]}{TuT}\Pr(X_i=1 | C_i=0) \\
        \quad &+ \frac{\mathbb{E}[Y_{1i}-Y_{0i}| C_i=0, X_i=0]}{TuT}\Pr(X_i=0 | C_i=0)
    \end{align*}

%and we will say that the variable $B_i$ explains the ToT whenever one of the terms (ratio weighted by the probability) is statistically significant from zero, (close to one), and the other term is statistically zero.
    \end{itemize}
}

@@

@@

\begin{frame}{Determinants of Sure Confidence}

        \begin{figure}
        \caption{What attributes correlate with Sure Confidence?}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/determinants_confidence_100.pdf}
        \end{figure}

The Sure-Confident are:
\begin{itemize}
    \item   Older, more educated men who
    \item   Have savings and do not report financial stress or trouble meeting bills, and 
    \item   Are likely to be relied upon by family members.
\end{itemize}

\begin{frame}{Understanding Heterogeneity with a Causal Forest}
\label{HTE}
\begin{itemize}

\item We use (Athey et.al. 2019) GRF to estimate CATE (causal RF), CTUT and CTOT (instrumental RF).

\begin{itemize}	
	\item We split the data that produce the biggest difference in TE across leaves, by still producing accurate estimates of the TE. Moreover, the splits are made honest by taking the training data and splitting it into two subsamples: a splitting subsample and an estimating subsample. \hyperlink{honest_causal_tree}{\beamerbutton{Honest Causal Tree}}   
\end{itemize}

\item Estimated TE in each leaf is aysmptotically normal. 
\end{itemize}

    \begin{figure}
        \caption{CATE (APR)}
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/he_dist_apr_pro_2.pdf}
        \end{figure}

 \begin{itemize}
\item We test and reject the null hypothesis of homogeneous treatment effects (Chernozhukov et. al. 2018)
 \end{itemize}       
\end{frame}

\begin{frame}{Example of a Causal Tree}

    \begin{figure}
        \caption{Causal Tree}
        \centering
\includegraphics[width=0.8\textwidth]{Figuras/ct_eff.pdf}
        \end{figure}

\begin{frame}{Fraction that forgo benefit:  Choice Arm}

        \begin{figure}
        \label{choose_wrong}
        \caption{Mistakes in choice arm}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_cw_apr_tot_tut.pdf}
        \end{figure}

\begin{itemize}
    \item   Use Random Forest to estimate ToT, TUT conditional on covariates.
    \item   Those making either choice make mistakes if benefit of other choice is higher.
    \item $>$ 70\% of non-choosers would have seen some benefit from assignment to commitment.
    \item  $<$ 20\% of choosers made a mistake.
\end{itemize}

\begin{frame}{Fraction that forgo benefit:  Forcing Arm}

        \begin{figure}
         \label{better_forceall}
        \caption{Effect of forcing everyone}
        \centering
        \includegraphics[width=0.65\textwidth]{Figuras/line_better_forceall_apr_te_cf.pdf}
        \end{figure}

\begin{itemize}
    \item   Now use Random Forest to estimate the CATE of forcing, examine heterogeneity in ATE.
    \item   Because CATE>CTUT, we now find fully 91\% of individuals better off being forced into commitment than staying in control.
\end{itemize}

\begin{frame}{How well can we target paternalism?}

\begin{itemize}
    \item   Why be paternalistic to everyone if we have a strong ability to predict those who lose and we can assign them to control?

     \vspace{.2in}

    \item   Standard targeting analysis, except need to consider covariates carefully given context.
    \item   Private sector lender, competitive market, part of attraction of pawning is no application!  
    \begin{itemize}
        \item Only use readily observable and non-falsifiable covariates.
    \item   Cannot use any behavioral covariates for which truthful reporting becomes non-incentive-compatible if incentivized.
    \item   Cannot use choice and then compel compliance among non-choosers in a commercial context.  
    \end{itemize}

     \vspace{.2in}

    \item Which leaves us with:
    \begin{itemize}
    \item   Age
    \item   Gender
    \item   HS Education or above
    \item   Ever pawned before 
    \end{itemize}

     \vspace{.2in}

    \item  We call these our `narrow' targeting criteria, while the full set of covariates used in the RF are `wide'.
\end{itemize}

\begin{frame}{Comparing `Wide' and `Narrow' Heterogeneity}

    \label{wide_v_narrow}

        \begin{figure}
        \caption{Scatterplot of Predicted Heterogeneity}
        \centering
        \includegraphics[width=0.75\textwidth]{Figuras/scatter_hist_wide_narrow.pdf}
        \end{figure}

\begin{itemize}
    \item   Substantially less heterogeneity fitting APR CATE with `narrow' than `wide'
    \item Test of homogeneity (Chernozhukov et. al. 2018) no longer rejected with `narrow'
    \item   However, overall fitted relationship shows `narrow' adjusts to the mean TE.
\end{itemize}

\begin{frame}{Comparison of Targeting Performance:  CDFs}

        \begin{figure}
        \label{targeting_CDFs}
        \caption{Distribution of Benefits under Different Targeting Rules}
        \centering
        \includegraphics[width=0.70\textwidth]{Figuras/wide_narrow_rule.pdf}
        \end{figure}

\begin{itemize}
    \item   Even using the Random Forest to target, our four `narrow' variables only increase the fraction benefitting from 91\% (all Forced) to ~93\% (targeted).
    \item  Using a Logit with the `narrow' variables actually worsens performance relative to universal Forcing because Logit matches benefit/loss fraction, has both Type 1 and Type 2 errors.
\end{itemize}

\begin{frame}{Comparison of Targeting Performance:  Hit-Miss Table}

\begin{table}[H]
\caption{Type I \& II errors using targeting narrow rules}
\label{hit_miss_rule}
\begin{center}
\resizebox{0.95\textwidth}{!}{
\small{\input{./Tables/hit_miss_rule.tex}}
}
\end{center}
\end{table}

\begin{itemize}
    \item   As seen above, even RF with `narrow' variables results in very modest increase in targeting efficiency relative to universal paternalism.
    \item  Logit performs very poorly because it makes symmetric Type I and Type II errors and hence assigns many to control who would have been better off with commitment.
    \item  \textbf{Takeaway:}  In this context, with these variables, targeting paternalism relatively ineffective.
\end{itemize}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
     \vfill \item Laibson has spoken of `veiled paternalism' in contexts where principals desire reliability; here we have a case of `veiled non-paternalism' where features encouraging default might be embedded.
     \vfill \item Novel design to study essential heterogeneity: ``Controlled Choice''
        %\begin{itemize}
         %   \item Combine ``Controlled Choice'' with MTE: Can we extend results of Mogstad et al (2017) to use our ATE, TUT, and TOT as additional inequality restrictions that constrain partial identification bounds for MTEs?
        %\end{itemize}
        \vfill \item  APR reduced by 34\% in the commitment arm
        \vfill  \item Results suggest selection on gains, but still large effects of imposing commitment on non-takers.
        \vfill \item Mystery of low take-up combined with large TuT seems best explained by sure-confidence among pawnshop customers.
        \vfill\item  Ability to target paternalism using objective covariates is poor; even using RF without cross-validation gains from targeting are small and with logit actually makes things worse.
        \vfill \item Suggests mandated commitment-based contract structures in payday/pawnshop loans as a form of pro-poor regulation?
    \end{itemize}  
\end{frame}

@@

@@

@@

\begin{frame}{Honest Causal Tree construction}
\label{honest_causal_tree}
Given a dataset with an outcome $Y$, covariates $X$, and a randomized condition $T$ that takes on the value of 0 for control and 1 for treatment:

\begin{enumerate}
\item Split the data into subsample $I$ and subsample $J$

\item Train a decision tree on subsample $I$ predicting $Y$ from $X$, with the requirement that each terminal node has at least $k$ observations from each condition in subsample $J$

\item Apply the decision tree constructed on subsample $I$ to subsample $J$

\item At each terminal node, get the mean of predictions for the $T = 1$ cases from subsample $J$ and subtract the mean of predictions for the $T = 0$ cases from subsample $J$; the resulting difference is the estimated treatment effect.

\end{enumerate}

This is then applied to a causal random forest by using bagging or bootstrapping.
\hyperlink{HTE}{\beamerbutton{Back}}\\
